Visualizations for article

### 2016-05-26 101-visualizations-for-article.Rmd
Fix colors, heights and selected codes

```{r setup,}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r fig.height=3}
spectrogram("CA1850", best_matches, white_list = 7)
```

@@

```{r fig.height=4}
spectrogram("CA1851", best_matches, white_list = 3)
```

@@

```{r, fig.height=2.5}
spectrogram("MD1855", best_matches, white_list = 7)
```

@@

```{r}
spectrogram("WA1855", best_matches, white_list = 8)
```

@@

```{r fig.height=4.5}
spectrogram("NV1861", best_matches, white_list = 4)
```

@@

```{r}
all_NV1861 <- data_frame(borrower_code = "NV1861",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "NV1861") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "NV1861",
         str_detect(match_code, "NY"),
         score >= 0.1,
         match_year <= 1861) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

@@

spectrogram("NV1861", NV1861toNY, white_list = 5,
            title = "Sections in NV1861 with high similarity to NY codes")
```

Like the previous query for NV1861, Iowa is two steps away from New York. This time, however, the text is much less similar to New York. I only want one visualization for this, but I'm not sure if IA1851 or the revision IA1859 will be better, so can we do both?

IA1851

```{r}
all_IA1851 <- data_frame(borrower_code = "IA1851",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "IA1851") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "IA1851",
         str_detect(match_code, "NY"),
         score >= 0.1,
         match_year <= 1851) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

IA1851toNY <- all_IA1851 %>% left_join(matches_to_NY) %>% 
  arrange(borrower_section)

spectrogram("IA1851", IA1851toNY, white_list = 10,
            title = "Sections in IA1851 with matches to NY codes")
```

@@

```{r}
all_IA1859 <- data_frame(borrower_code = "IA1859",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "IA1859") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "IA1859",
         str_detect(match_code, "NY"),
         score >= 0.1,
         match_year <= 1859) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

@@

```{r}
spectrogram("NC1868", best_matches, white_list = 8)
```

@@

```{r}
spectrogram("CO1868", best_matches, white_list = 8)
```

Same query as number 6 and 7, but like Louisiana, the point is to show that no one borrows the later New York Code, the one that departs from the Field tradition.

```{r, fig.height=6.5}
spectrogram("NY1876", best_matches, white_list = 8)
```

```{r, fig.height=7.75}
spectrogram("NY1879", best_matches, white_list = 3)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r ca1850-borrowings, fig.height=3}
spectrogram("CA1850", best_matches, white_list = c("LA1844", "NY1829", "NY1849",
                                                   "NY1848"))
```

@@

```{r CA1851-borrowings, fig.height=3.5}
spectrogram("CA1851", best_matches, white_list = 3)
```

@@

```{r MD1855-borrowings, fig.height=2.5}
spectrogram("MD1855", best_matches, white_list = c("GB1852"))
```

@@

```{r WA1855-borrowings, fig.height=4.5}
spectrogram("WA1855", best_matches, white_list = c("CA1850", "CA1851", "IN1852",
                                                   "NY1853", "OR1854", "WI1849"))
```

@@

```{r NV1861-borrowings, fig.height=4.5}
spectrogram("NV1861", best_matches, white_list = 5)
```

@@

```{r NV1861-to-NY, fig.height=4.5}
all_NV1861 <- data_frame(borrower_code = "NV1861",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "NV1861") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "NV1861",
         str_detect(match_code, "NY"),
         match_code != "NY1829",
         score >= 0.1,
         match_year <= 1861) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

@@

spectrogram("NV1861", NV1861toNY, white_list = 7,
            title = "Sections in NV1861 with high similarity to NY codes")
```

@@

```{r IA1859-to-NY}
all_IA1859 <- data_frame(borrower_code = "IA1859",
                         borrower_section = all_matches %>% 
                           filter(borrower_code == "IA1859") %>% 
                           `$`("borrower_section") %>%
                           unique() %>%
                           sort()
                        )

matches_to_NY <- all_matches %>% 
  filter(borrower_code == "IA1859",
         str_detect(match_code, "NY"),
         match_code != "NY1829",
         score >= 0.1,
         match_year <= 1859) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup()

@@

```{r NC1868-matches}
spectrogram("NC1868", best_matches, white_list = c("CA1858", "OR1862", "MN1859",
                                                   "NY1849", "CA1850", "WI1858",
                                                   "NY1853", "NY1851", "NY1850",
                                                   "WI1856"))
```

@@

```{r CO1868-matches, fig.height=3.5}
spectrogram("CO1868", best_matches, white_list = c("IL1866"))
```

CO1877: companion visualization of Colorado under the Field code

```{r CO1877-matches, fig.height=4}
spectrogram("CO1877", best_matches, white_list = 8) 
```

MT 1895

```{r MT1895-matches, fig.height=7.5}
spectrogram("MT1895", best_matches, white_list = 8)
```

NY1876

```{r NY1876-matches, fig.height=6.5}
spectrogram("NY1876", best_matches, white_list = c("NY1829", "NY1850", "NY1853",
                                                   "NY1848", "NY1849", "NY1851"))
```

NY1879

```{r NY1879-matches, fig.height=7}
spectrogram("NY1879", best_matches, white_list = c("NY1853", "NY1876"))
```
